Introduction to *cellcount* - Draft vignette

### 2023-04-20 cellcount_intro.Rmd
New additions/changes made

```{r,message=FALSE}
savdir <- ("C:/file path for saving CSV data")
image_savdir <- ("C:/file path for saving converted images")
```
```{r,include=FALSE}
savdir <- ("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_data/")
image_savdir <- ("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_results/")
```

@@

```{r,message=FALSE}
images <- list.files("C:/file path of images to analyze", pattern = "tif", full.name = T)
images_names <- list.files("C:/file path of images to analyze", pattern = "tif", full.name = F)
```
```{r,include=FALSE}
images <- list.files("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_images/Microcystis_F192_40x/", pattern = "tif", full.name = T)
images_names <- list.files("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_images/Microcystis_F192_40x/", pattern = "tif", full.name = F)
```

@@

```{r,echo=FALSE}
display(final_img)
Cell.Count
```
Test data results for *Microcystis* strain F-192
<br>
<br>
<br>
<br>

@@

```{r,include=FALSE}
greyscale <- function(x, contrast = 2) {
  x <- contrast * x
  x <- x[, , 1] + x[, , 2] + x[, , 3]
  x <- x / max(x)
  x <- normalize(x, inputRange = c(0.1, 0.75))
  return(x)
}
mapped <- function(x, threshold = 0.3) {
  x <- as.matrix(x)
  x[x < threshold] <- 0
  return(x)
}
border <- function(x, y) {
  c(x[1:y[1], 1], x[1:y[1], y[2]], x[1, 1:y[2]], x[y[1], 1:y[2]])
}
count_cells <- function(x) {
  countAll <- max(x)
  dims <- dim(x)
  border1 <- border(x, dims)
  ids <- unique(border1[which(border1 != 0)])
  countInner <- countAll - length(ids)
  return(countInner)
}
count_images <- function(image, normalize = TRUE, removeEdgeCells = TRUE) {
  if (removeEdgeCells) {
    dims <- dim(image)
    border1 <- border(image, dims)
    ids <- unique(border1[which(border1 != 0)])
    inner <- rmObjects(image, ids)
    EBImage::colorLabels(inner, normalize = normalize)
  } else {
    EBImage::colorLabels(image, normalize = normalize)
  }
}
single_cell_convert <- function(x, w = 17, h = 17, offset = 0.001, areathresh = 50, tolerance= 0.5, ext = 1) {
  image <- thresh(x, w = w, h = h, offset = offset)
  image1 <- fillHull(image)
  image2 <- watershed(distmap(image1), tolerance = tolerance, ext = ext)
  nf <- computeFeatures.shape(image2)
  nr <- which(nf[, "s.area"] < areathresh)
  image3 <- rmObjects(image2, nr)
  return(image3)
}
filamentous_convert <- function(x, w = 17, h = 17, offset = 0.001, areathresh = 50, tolerance= 0.5, ext = 1) {
  image <- thresh(x, w = w, h = h, offset = offset)
  image1 <- watershed(distmap(image), tolerance = tolerance, ext = ext)
  image2 <- fillHull(image1)
  nf <- computeFeatures.shape(image2)
  nr <- which(nf[, "s.area"] < areathresh)
  image3 <- rmObjects(image2, nr)
  return(image3)
}
cell_density <- function(x, FOV = 0.0726, images = 10, filtration.area = 213.8, volume = 1, total.volume = 5) {
  MCF <- filtration.area / FOV
  N <- x / images
  cyano <- (MCF * N) / volume
  cyano_total <- cyano * total.volume
  return(cyano_total)
}
outlier_detect<-function(){
  mean<-median(Cell.Count$Cell_Count)
  sd<-sd(Cell.Count$Cell_Count)*2
  sd_neg<-(mean-sd)
  sd_pos<-(mean+sd)
  SD_range_detection<-ifelse(sd_pos>Cell.Count$Cell_Count,Cell.Count$Cell_Count,NA)&
    ifelse(sd_neg<Cell.Count$Cell_Count,Cell.Count$Cell_Count,NA)
  return(SD_range_detection)
}
```

@@

savdir <- ("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_data/")
image_savdir <- ("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_results/")
images <- list.files("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_images/NZ_Anabena_60x/", pattern = "tif", full.name = T)
images_names <- list.files("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_images/NZ_Anabena_60x/", pattern = "tif", full.name = F)

@@

Cell.Count
```
Test data results for *Anabena* sp.
<br>
<br>
<br>
<br>

@@

```{r,include=FALSE}
greyscale <- function(x, contrast = 2) {
  x <- contrast * x
  x <- x[, , 1] + x[, , 2] + x[, , 3]
  x <- x / max(x)
  x <- normalize(x, inputRange = c(0.1, 0.75))
  return(x)
}
mapped <- function(x, threshold = 0.3) {
  x <- as.matrix(x)
  x[x < threshold] <- 0
  return(x)
}
border <- function(x, y) {
  c(x[1:y[1], 1], x[1:y[1], y[2]], x[1, 1:y[2]], x[y[1], 1:y[2]])
}
count_cells <- function(x) {
  countAll <- max(x)
  dims <- dim(x)
  border1 <- border(x, dims)
  ids <- unique(border1[which(border1 != 0)])
  countInner <- countAll - length(ids)
  return(countInner)
}
count_images <- function(image, normalize = TRUE, removeEdgeCells = TRUE) {
  if (removeEdgeCells) {
    dims <- dim(image)
    border1 <- border(image, dims)
    ids <- unique(border1[which(border1 != 0)])
    inner <- rmObjects(image, ids)
    EBImage::colorLabels(inner, normalize = normalize)
  } else {
    EBImage::colorLabels(image, normalize = normalize)
  }
}
single_cell_convert <- function(x, w = 17, h = 17, offset = 0.001, areathresh = 50, tolerance= 0.5, ext = 1) {
  image <- thresh(x, w = w, h = h, offset = offset)
  image1 <- fillHull(image)
  image2 <- watershed(distmap(image1), tolerance = tolerance, ext = ext)
  nf <- computeFeatures.shape(image2)
  nr <- which(nf[, "s.area"] < areathresh)
  image3 <- rmObjects(image2, nr)
  return(image3)
}
filamentous_convert <- function(x, w = 17, h = 17, offset = 0.001, areathresh = 50, tolerance= 0.5, ext = 1) {
  image <- thresh(x, w = w, h = h, offset = offset)
  image1 <- watershed(distmap(image), tolerance = tolerance, ext = ext)
  image2 <- fillHull(image1)
  nf <- computeFeatures.shape(image2)
  nr <- which(nf[, "s.area"] < areathresh)
  image3 <- rmObjects(image2, nr)
  return(image3)
}
cell_density <- function(x, FOV = 0.0726, images = 10, filtration.area = 213.8, volume = 1, total.volume = 5) {
  MCF <- filtration.area / FOV
  N <- x / images
  cyano <- (MCF * N) / volume
  cyano_total <- cyano * total.volume
  return(cyano_total)
}
outlier_detect<-function(){
  mean<-median(Cell.Count$Cell_Count)
  sd<-sd(Cell.Count$Cell_Count)*2
  sd_neg<-(mean-sd)
  sd_pos<-(mean+sd)
  SD_range_detection<-ifelse(sd_pos>Cell.Count$Cell_Count,Cell.Count$Cell_Count,NA)&
    ifelse(sd_neg<Cell.Count$Cell_Count,Cell.Count$Cell_Count,NA)
  return(SD_range_detection)
}
```

@@

savdir <- ("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_data/")
image_savdir <- ("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_results/")
images <- list.files("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = T)
images_names <- list.files("C:/Users/Tyler.Harman/Desktop/cellcount_work/cellcount_main/test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = F)

@@

Cell.Count
```
Test data results for *Shewanella* IRI-160

@@

The *input_data_GUI* function generates a Shiny UI where users enter information regarding directories, numerical and categorical data, 
and selecting analysis type. Tabs to the left of the UI separate particular categories for easy organization. Once all data has been
provided, users complete the input of data by selecting the "Completion" tab and clicking the "Submit data entries" button to export 
data to the local R environment.

@@

<br>

>>>>

```{r,message=FALSE}
savdir <- ("C:/file path for saving CSV data")
image_savdir <- ("C:/file path for saving converted images")
```
```{r,include=FALSE}
savdir <- ("./test_data/")
image_savdir <- ("./test_results/")
```

@@

```{r,message=FALSE}
images <- list.files("C:/file path of images to analyze", pattern = "tif", full.name = T)
images_names <- list.files("C:/file path of images to analyze", pattern = "tif", full.name = F)
```
```{r,include=FALSE}
images <- list.files("./test_images/Microcystis_F192_40x/", pattern = "tif", full.name = T)
images_names <- list.files("./test_images/Microcystis_F192_40x/", pattern = "tif", full.name = F)
```

@@

### Test data results for *Microcystis* strain F-192
```{r,echo=FALSE}
display(final_img)
Cell.Count
```
<br>
<br>

@@

### Test data results for *Anabena* sp.
```{r,include=FALSE}
greyscale <- function(x, contrast = 2) {
  x <- contrast * x
  x <- x[, , 1] + x[, , 2] + x[, , 3]
  x <- x / max(x)
  x <- normalize(x, inputRange = c(0.1, 0.75))
  return(x)
}
mapped <- function(x, threshold = 0.3) {
  x <- as.matrix(x)
  x[x < threshold] <- 0
  return(x)
}
border <- function(x, y) {
  c(x[1:y[1], 1], x[1:y[1], y[2]], x[1, 1:y[2]], x[y[1], 1:y[2]])
}
count_cells <- function(x) {
  countAll <- max(x)
  dims <- dim(x)
  border1 <- border(x, dims)
  ids <- unique(border1[which(border1 != 0)])
  countInner <- countAll - length(ids)
  return(countInner)
}
count_images <- function(image, normalize = TRUE, removeEdgeCells = TRUE) {
  if (removeEdgeCells) {
    dims <- dim(image)
    border1 <- border(image, dims)
    ids <- unique(border1[which(border1 != 0)])
    inner <- rmObjects(image, ids)
    EBImage::colorLabels(inner, normalize = normalize)
  } else {
    EBImage::colorLabels(image, normalize = normalize)
  }
}
single_cell_convert <- function(x, w = 17, h = 17, offset = 0.001, areathresh = 50, tolerance= 0.5, ext = 1) {
  image <- thresh(x, w = w, h = h, offset = offset)
  image1 <- fillHull(image)
  image2 <- watershed(distmap(image1), tolerance = tolerance, ext = ext)
  nf <- computeFeatures.shape(image2)
  nr <- which(nf[, "s.area"] < areathresh)
  image3 <- rmObjects(image2, nr)
  return(image3)
}
filamentous_convert <- function(x, w = 17, h = 17, offset = 0.001, areathresh = 50, tolerance= 0.5, ext = 1) {
  image <- thresh(x, w = w, h = h, offset = offset)
  image1 <- watershed(distmap(image), tolerance = tolerance, ext = ext)
  image2 <- fillHull(image1)
  nf <- computeFeatures.shape(image2)
  nr <- which(nf[, "s.area"] < areathresh)
  image3 <- rmObjects(image2, nr)
  return(image3)
}
cell_density <- function(x, FOV = 0.0726, images = 10, filtration.area = 213.8, volume = 1, total.volume = 5) {
  MCF <- filtration.area / FOV
  N <- x / images
  cyano <- (MCF * N) / volume
  cyano_total <- cyano * total.volume
  return(cyano_total)
}
outlier_detect<-function(){
  mean<-median(Cell.Count$Cell_Count)
  sd<-sd(Cell.Count$Cell_Count)*2
  sd_neg<-(mean-sd)
  sd_pos<-(mean+sd)
  SD_range_detection<-ifelse(sd_pos>Cell.Count$Cell_Count,Cell.Count$Cell_Count,NA)&
    ifelse(sd_neg<Cell.Count$Cell_Count,Cell.Count$Cell_Count,NA)
  return(SD_range_detection)
}
```

@@

savdir <- ("./test_data/")
image_savdir <- ("./test_results/")
images <- list.files("./test_images/NZ_Anabena_60x/", pattern = "tif", full.name = T)
images_names <- list.files("./test_images/NZ_Anabena_60x/", pattern = "tif", full.name = F)

@@

Cell.Count
```
<br>
<br>

@@

### Test data results for *Shewanella* IRI-160
```{r,include=FALSE}
greyscale <- function(x, contrast = 2) {
  x <- contrast * x
  x <- x[, , 1] + x[, , 2] + x[, , 3]
  x <- x / max(x)
  x <- normalize(x, inputRange = c(0.1, 0.75))
  return(x)
}
mapped <- function(x, threshold = 0.3) {
  x <- as.matrix(x)
  x[x < threshold] <- 0
  return(x)
}
border <- function(x, y) {
  c(x[1:y[1], 1], x[1:y[1], y[2]], x[1, 1:y[2]], x[y[1], 1:y[2]])
}
count_cells <- function(x) {
  countAll <- max(x)
  dims <- dim(x)
  border1 <- border(x, dims)
  ids <- unique(border1[which(border1 != 0)])
  countInner <- countAll - length(ids)
  return(countInner)
}
count_images <- function(image, normalize = TRUE, removeEdgeCells = TRUE) {
  if (removeEdgeCells) {
    dims <- dim(image)
    border1 <- border(image, dims)
    ids <- unique(border1[which(border1 != 0)])
    inner <- rmObjects(image, ids)
    EBImage::colorLabels(inner, normalize = normalize)
  } else {
    EBImage::colorLabels(image, normalize = normalize)
  }
}
single_cell_convert <- function(x, w = 17, h = 17, offset = 0.001, areathresh = 50, tolerance= 0.5, ext = 1) {
  image <- thresh(x, w = w, h = h, offset = offset)
  image1 <- fillHull(image)
  image2 <- watershed(distmap(image1), tolerance = tolerance, ext = ext)
  nf <- computeFeatures.shape(image2)
  nr <- which(nf[, "s.area"] < areathresh)
  image3 <- rmObjects(image2, nr)
  return(image3)
}
filamentous_convert <- function(x, w = 17, h = 17, offset = 0.001, areathresh = 50, tolerance= 0.5, ext = 1) {
  image <- thresh(x, w = w, h = h, offset = offset)
  image1 <- watershed(distmap(image), tolerance = tolerance, ext = ext)
  image2 <- fillHull(image1)
  nf <- computeFeatures.shape(image2)
  nr <- which(nf[, "s.area"] < areathresh)
  image3 <- rmObjects(image2, nr)
  return(image3)
}
cell_density <- function(x, FOV = 0.0726, images = 10, filtration.area = 213.8, volume = 1, total.volume = 5) {
  MCF <- filtration.area / FOV
  N <- x / images
  cyano <- (MCF * N) / volume
  cyano_total <- cyano * total.volume
  return(cyano_total)
}
outlier_detect<-function(){
  mean<-median(Cell.Count$Cell_Count)
  sd<-sd(Cell.Count$Cell_Count)*2
  sd_neg<-(mean-sd)
  sd_pos<-(mean+sd)
  SD_range_detection<-ifelse(sd_pos>Cell.Count$Cell_Count,Cell.Count$Cell_Count,NA)&
    ifelse(sd_neg<Cell.Count$Cell_Count,Cell.Count$Cell_Count,NA)
  return(SD_range_detection)
}
```

@@

savdir <- ("./test_data/")
image_savdir <- ("./test_results/")
images <- list.files("./test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = T)
images_names <- list.files("./test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = F)

@@

Cell.Count
```

@@

### Inputting data
The *input_data_GUI* function generates a Shiny UI where users enter information regarding directories, numerical and categorical data, 
and selecting analysis type. Tabs to the left of the UI separate particular categories for easy organization. Once all data has been
provided, users complete the input of data by selecting the "Completion" tab and clicking the "Submit data entries" button to export 
data to the local R environment.

@@

### Running the image analysis
